Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-07-29 paper/ms.tex
minor abstract changes

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$, by comparing the number density and the angular
correlation function between mock and observed fields. The mock fields
are constructed in a large cosmological N-body simulation using a
model where a dark matter halo can only host one LAE with a
probability $f_{\rm occ}$  if its mass is within the mass range
delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
define three different families of parameters consistent with
observations based on their mass range
$\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
fraction $f_{\rm occ}$.  From this we conclude that the number
density and spatial clustering information available from observations
is not sufficient to derive a unique and narrow set of values for the
parameters in the model. In particular, it is always possible to find a 
a model with any desired occupation fraction in the range $0.1\leq
f_{\rm occ}\leq 1.0$.  However, there is a dominant family composed by
models with a narrow mass range $\Delta M<1.0$ dex, a low occupation fraction
$f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm   max}<
10^{12}$\hMsun.  This suggests that the most massive dark matter halos
at that epoch do not host the brightest LAEs, also giving support to
some observational evidence indicating that only a small fraction of
star forming galaxies can be actually detected as LAEs. We provide
tables and mock catalogs for the successful models.   
\end{abstract}

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$, by comparing the number density and the angular
correlation function between mock and observed fields. The mock fields
are constructed in a large cosmological N-body simulation using a
model where a dark matter halo with mass in the range $M_{\rm
  min}<M_{\rm h}<M_{\rm max}$ can only host one LAE with a
probability $f_{\rm occ}$. We define three different families of
parameters consistent with observations based on their mass range
$\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
fraction $f_{\rm occ}$.  From this we conclude that the number
density and spatial clustering information available from observations
is not sufficient to derive a unique and narrow set of values for the
parameters in the model. In particular, it is always possible to find a 
a model with any desired occupation fraction in the range $0.1\leq
f_{\rm occ}\leq 1.0$.  However, there is a dominant family composed by
models with a narrow mass range $\Delta M<1.0$ dex, a low occupation fraction
$f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm   max}<
10^{12}$\hMsun.  The existence of this dominant family gives support
to the idea that the most massive dark matter halos at that epoch do
not host the brightest LAEs and that only a small fraction of star
forming galaxies can be actually detected as LAEs.

\end{abstract}
